\documentclass[a4paper,9pt]{article}

%Packages
\usepackage[english]{babel}
\usepackage{titlesec}
\usepackage{blindtext}
\usepackage{microtype}
\usepackage{booktabs}
\usepackage{placeins}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{xhfill}
\usepackage{multicol}
\usepackage{dirtytalk}
\usepackage{tabularx}
\usepackage[hidelinks]{hyperref}
\usepackage[margin=0.25in]{geometry}

%Section Formatting
% \titlespacing{\section}{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}

\titleformat{\section}
    {\Large\bfseries}{\filright\footnotesize\enspace SECTION\thesection\enspace}{12pt}
    {\titlerule[1.0pt]}

\titleformat{\subsection}
    {\normalfont\bfseries}{\thesection}{1em}{}
    % [{\titlerule[0.8pt]}]

\setlength{\parindent}{0pt}%

\pagenumbering{gobble}
\date{}

\begin{document}

\section*{Filip Livancic}

\begin{itemize}[noitemsep]
    \item\textbf{Location: }East Finchley, London
    \item\textbf{Email: }\href{mailto:filiplivancic@gmail.com}{filiplivancic@gmail.com}
    \item\textbf{Mobile: }+44 740 346 7511
    \item\textbf{Github: }\url{https://github.com/Filpill/}
    \item\textbf{Website: }\url{https://filiplivancic.com/}
    \item\textbf{LinkedIn: }\url{https://www.linkedin.com/in/filip-livancic/}
\end{itemize}


\section*{Skills}
\subsection*{Technical Skills}
\begin{itemize}[noitemsep]
    \item \textbf{Cloud:} \hspace{17mm} Google Cloud Platform (GCP)
	\item \textbf{Python:} \hspace{14.8mm} Pandas, Numpy, Matplotlib, Xlsxwriter, Python-pptx, Pyodbc
	\item \textbf{Command Line:} \hspace{0.5mm} Arch Linux, GCloud, Git, GitHub, Shell(bash/zsh)
	\item \textbf{Programming:} \hspace{3.3mm} HTML, CSS, Hugo, MATLAB, Python, Shell, SQL
	\item \textbf{Data Analytics:} \hspace{1mm} Microsoft SQL Server, BigQuery, Tableau, Python, Excel
    \item \textbf{Documentation:} \hspace{0.5mm} Microsoft Office: Word, Excel, Powerpoint, Visio
	\item \textbf{Miscellaneous:} \hspace{3.3mm} GIMP, LaTeX, Markdown, SolidWorks, Vim
	\item \textbf{Languages:} \hspace{9.3mm} English(Native), Croatian(Native), French(Basic)
\end{itemize}

%Work Experience
\section*{Work Experience}
\subsection*{\textbf{Sky - Data Visualisation Engineer} \hfill  Dec 2022 - Present}
\begin{itemize}[noitemsep]

    \item Coordinating with stakeholders in translating business requirements into new Tableau Reporting Solutions.
    \item Writing and optimising SQL stored procedures in BigQuery to serve back-end tables for multiple Tableau reports.
    \item Migrating legacy reports and analytics focusing on broadband products using BigQuery and Tableau infrastructure.
    \item Building new broadband contract analysis KPI's: e.g. churn rates, discounts, or post-notification actions for end of contract.

\end{itemize}

\subsection*{\textbf{easyJet - Safety Data Analyst} \hfill  Nov 2021 - Nov 2022}
\begin{itemize}[noitemsep]
	\item Creating end-to-end data pipelines: data ingestion with Pyodbc into DataFrames for data analytics in Pandas.
	\item Automating data analysis execution with python scripts executed with batch files and exporting Excel's with Xlsxwriter.
	\item Automating PowerPoints' with python-pptx refreshing over 12 presentation packs (450 tailor-made slides) in under 1 minute.
	\item Creating Tableau dashboards which query from multiple SQL database systems and consolidate safety performance indicators.
    \item Connecting safety reporting data with operational flight data using Tableau relationships to apply statistical normalization.


%	\item \textbf{Creating end-to-end data pipelines}: data ingestion with \textbf{Pyodbc (via T-SQL query)}, data cleaning with \textbf{Pandas} and exporting Excel dashboards with \textbf{Xlsxwriter}.
%	\item \textbf{Automating data} analysis execution with \textbf{python} scripts via batch files with \textbf{up to +99\% efficiency in exec. time.}
%	\item \textbf{Automating PowerPoints'} with \textbf{python-pptx}: refreshing over \textbf{12 presentation packs (450 tailor-made slides) in under 1 minute.}
%
%	\item Creating \textbf{Tableau dashboards} which query from \textbf{multiple SQL database systems}: connecting safety reporting data with operational flight data using \textbf{Tableau relationships.}
%	\item Communicating with stakeholders; \textbf{providing safety performance indicators} and identifying gaps in data capture.


\end{itemize}

\subsection*{\textbf{TUI Airways - Engineering Safety Analyst} \hfill  Aug 2018 - Sept 2021}
\begin{itemize}[noitemsep]
	\item Coordinating engineering investigations to generate root cause analysis and assure effective occurrence risk management.
	\item Leading discussions in the Engineering Safety Action Group, and presenting data to drive risk mitigation actions.
	\item Designing occurrence reporting process flows with high clarity using Visio and in compliance with airline safety regulations.
	\item Harnessing Pandas and Matplotlib to create data-sets to monitor E\&M reporting metrics within the airlines safety system.
	\item Building Excel Dashboards to automate workflow and monitor safety performance indicators for the engineering department.
\end{itemize}

%\subsection*{\textbf{Booker Gliding Club – Cadet (Volunteer)}\hfill Feb 2013 - Jul 2018}
%\begin{itemize}[noitemsep]
%
%	\item Supporting gliding operation at airfield by minimising flying aircraft downtime and ensuring efficient ground movements.
%	\item Performing launch point preparation, flight log administration, glider launching and retrieval.
%
%\end{itemize}


\section*{Data Projects}

\subsection*{\textbf{Data Projects Website}: \url{https://filpill.github.io} \hfill  May 2022 – Present}
\begin{itemize}[noitemsep]

	\item  Porting legacy project website written in manual HTML and CSS to Hugo framework and maintain pages with markdown.
	\item  Developing data skills with Python: sourcing data-sets from public API's, performing data cleansing and visualisations.
	\item  Incorporating git tools to manage version control of projects and hosting website using Github pages.

\end{itemize}

%\subsection*{\textbf{Python Project - 2D Unsteady Heat Transfer Simulation }\hfill  Jun 2021 – Jul 2021}
%
%\begin{itemize}[noitemsep]
%    \item Discretized heat equation, generalised the mesh for any dimensions and resolved using successive over relaxation solver.
%    \item Evaluated an approximate solution of temperatures on the grid at each time step using the finite differencing method.
%    \item Captured animation of temperature progression over mesh using function in matplotlib and stored result as gif image.
%
%\end{itemize}

%\subsection*{\textbf{Arduino Project - 3D Printed Bluetooth Car } \hfill  Apr 2020 – Jun 2021}
%\begin{itemize}[noitemsep]
%	\item  Designed car with Solidworks, sliced STL's using Cura, printed parts on Ender 3 printer and assembled hand.
%	\item  Created Bluetooth serial communications system in Arduino and implemented GUI interface between PC and Arduino.
%
%\end{itemize}
%
%\subsection*{\textbf{UAV Design Project - Payload Challenge - Project Engineer } \hfill  Oct 2017 – Jul 2018}

%\begin{itemize}[noitemsep]
%	\item Defined system requirements and aircraft sizing in addition to coordinating aero/structures analysis with detailed design.
% 	\item Optimised aircraft configuration at conceptual design stage using Monte Carlo style simulation to maximise mission score.
%	\item Coordinated manufacture processes of UAV aircraft staged out into sub-systems and supplemented with building procedures.
%
%\end{itemize}

%\subsection*{\textbf{Aerodynamics Dissertation} \hfill  Sep 2016 – Jun 2017}
%
%
%\begin{itemize}[noitemsep]
%    \item \textbf{Experimental Study of Flow Separation on Forward Facing Step - PIV Measurements}
%	\item Designing test apparatus - enabling airflow illumination in preparation for wind tunnel testing.
%	\item MATLAB - Cross correlation of images, visualised velocity field and studied boundary layer.
%\end{itemize}

%\section*{Skills}
%\subsection*{Technical Skills}
%\begin{itemize}[noitemsep]
%    \item \textbf{Software:} Artix Linux, AMOS,  AutoCAD, Cura, MS SQL Server, SolidWorks,Tableau, XFLR5
%    \item \textbf{Documentation:}  Microsoft Office (Word/Excel/Powerpoint/Visio), LaTeX, Markdown, Vim
%    \item \textbf{Programming:}  Arduino, GitHub, HTML/CSS, Hugo, MATLAB, Python, SQL, VBA
%    \item \textbf{Other:} 3D Printing, UK Driving License, BGA Bronze Badge,HF Investigator
%    \item \textbf{Languages:} English(Fluent), Croatian(Native), French(Basic)
%\end{itemize}


\section*{Education}
\subsection*{\textbf {City, University of London - Aeronautical Engineering (MEng)}  \hfill Oct 2014 - Jul 2018}\FloatBarrier
\begin{itemize}[noitemsep]
	\item \textbf{Overall grade:} First Class Honours %70.3%
	\item \textbf{Scholarships:} George Daniels Scholarship - Sept 2015
\item \textbf{Relevant Modules:} Mathematics, Computing, and Systems Engineering
\end{itemize}


\subsection*{\textbf{St Gregory’s RC Science College} \hfill  Sep 2007 – Jul 2014}
\begin{itemize}[noitemsep]
    \item \textbf{A Level's:} Physics (A), Mathematics (B), Further Mathematics (B), Chemistry (C)
    \item \textbf{GCSE’s:} 11 GCSE’s (A*-C) Including English and Math
\end{itemize}

% \begin{itemize}[noitemsep]
% Advanced Aerodynamics and Propulsion
% Airworthiness and Maintenance
% Flight Dynamics
% Structural Dynamics and Aero-elasticity
% Systems Engineering
% UAV Design
% Engineering Management
% Fluid Mechanics
% Gas Turbine Engineering
% Mathematics and Computing
% Structural Analysis/Finite Element Method
% Thermodynamics
% \end{itemize}


\pagenumbering{gobble}
\date{}


\end{document}
